---
title: "My Shiny App"
author: "Sarah"
date: "9/13/2019"
output: ioslides_presentation
---

## Brief Description

* Limited by my own lack of creativity, I decided to make an app that shows the population of the different countries of the world.

Here's just a glimpse of the dataset

```{r popdata}
library(tidyr)
data("population")
summary(population)
```

## Interesting Population Trend 1

It's actually quite cool to look and see the trends of the different countries populations. For example: American Samoa

```{r asamoa, echo=FALSE}
asam<-subset(population,country == "American Samoa")
plot(asam$year, asam$population, xlab = "Year", ylab = "Population", main = "Population of American Samoa")
```

## Interesting Population Trend 2

Or here's another one: Andorra (It's the country on the border of France and Spain)
```{r andorra, echo = FALSE}
ando<-subset(population,country == "Andorra")
plot(ando$year, ando$population, xlab = "Year", ylab = "Population", main = "Population of Andorra")
```

##
#### In conclusion, my shiny app is really cool to see the population of different countries


###Thanks for the review!